---
title: "What is Lignin?"
categories:
  - Review
description: "Let's understand why lignin is gaining substantial importance in the academic and industrial areas."
base_url: https://datachemistry.github.io/lignum/posts/2021-01-02-what-is-lignin/
author:
  - first_name: "Thiago"
    last_name: "Yuki"
    url: https://github.com/datachemistry
    affiliation: University of São Paulo
    affiliation_url: https://sites.usp.br/phdbioenergy/
    orcid_id: 0000-0002-2476-3497
date: 01-02-2021
output:
  distill::distill_article:
    toc: true
    toc_float: true
    self_contained: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at <https://rstudio.github.io/distill>.

# Intro


What is Lignin?
Review
Introduction
Let’s understand why lignin is gaining substantial importance in the academic and industrial areas.

AUTHOR
AFFILIATION
Thiago Yuki ORCID ID

University of São Paulo

PUBLISHED
Jan. 2, 2021

Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at https://rstudio.github.io/distill.

# Teste

```{r teste, layout="l-body-outset", preview=TRUE}
library(ggplot2)
ggplot(diamonds, aes(carat, price)) + geom_smooth() +
  facet_grid(~ cut)
```


